Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-25 journal/article.tex
S: Have social events

>>>>

% Have social events

Social events were reported to benefit the transformation. A few cases even
described a the transformation being driven by a series of events where people
received information and had the possibility to participate in shaping the new
model of working [P32, P41]. Various social activities were presented as
valuable tools for improving bonding within teams [P11, P27, P40]. The importance of
creating personal bonding was also highlighted for change leading entities such
as management and coaching teams [P11, P23].
